Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2015-01-30 draft_lm1.tex
initial version of abstract

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
Our paper is just awesome.
% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}

>>>>

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
A method for estimation of the Attack ratio of an epidemic and the initial 
fraction of susceptibles, $S_0$, is proposed. The estimation methods obtain the 
Bayesian posterior distributions of the parameters by fitting a 
single-strain SIR transmission model with time-varying force of infection to 
the aggregated incidence data.  The data consists of 18 years of dengue 
incidence in the city of Rio de Janeiro, Brazil. An analytical method for 
deriving the probability distribution of the effective reproductive number, \rr.
\section*{Author Summary}
